Approximation as Differentiation notes

### 2025-02-26 notes/sec/set-indexed-product.tex
First pass over set-indexed products.

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ and family of morphisms $\eval_i$ in $C$ such that for any object
$Y$ of $C$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there exists a unique morphism
$\lambda f$ making the following diagram commute:

\begin{center}
\begin{tikzcd}
   \prod_{i \in I}X_i \arrow[r, "\eval_i"] &
   X_i
   \\
   Y \arrow[ru, "f_i"'] \arrow[u, "\lambda f"]
\end{tikzcd}
\end{center}

>>>>

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ and family of morphisms $\eval_i$ in $C$ such that for any object
$Y$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there exists a unique morphism $\lambda
f$ making the following diagram commute:

\begin{center}
\begin{tikzcd}
   \prod_{i \in I}X_i \arrow[r, "\eval_i"] &
   X_i
   \\
   Y \arrow[ru, "f_i"'] \arrow[u, dotted, "\lambda f"]
\end{tikzcd}
\end{center}
